Literature

### 2015-08-04 literature/literature.Rmd
started with a review reading

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
cat(paste0("##", citet(refs[["yang_alignment_2013"]])))
```

Don't understand. K0mer based, may be used for phylogenetics. Does not require specyfying $k$.

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
cat(paste0("##", citet(refs[["bonham-carter_alignment-free_2014"]])))
```

Good review. Description of: factor frequencies, BBC (mutual information of DNA 2-grams), FFP (number of words commong among two sequences), Jensen-Shannon Divergence test (a test using Kullback-Leibler Divergence), suffix trees by k-mer frequencies (Euclidean distance between frequency counts, get optimum $k$ called $l$), improved complete composition vector (distance between normalized frequency of positioned k-mers with different $k$),
